Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-08 R0V0.tex
Change notation of the curves from \gamma to c.
Write a small paragraph on how the energy function is a CLF.

Write a paragraph about SDD matrices

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{align*}
	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;,
\end{align*}
where the notation $\gamma_s$ stands for the derivative $\tfrac{\partial\gamma}{\partial s}$. The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
\end{equation}

@@

Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them. This implies that the solution $k^\ast$ to the integral equation
\begin{equation}\label{eq:contracting feedback law}
	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(s),k^\ast(t,s))\gamma_s(s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\frac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
	\end{equation}

	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$. Consequently,
	\begin{equation*}
		\gamma_i=\arg\inf e(\varphi_i)\Leftrightarrow\gamma=\arg\inf\ell(\varphi),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{equation*}
	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.

	From Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
	\begin{align*}
		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i)\;.
	\end{align*}
	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.

@@

	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma_s(s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

@@

	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\frac{\partial\widetilde{\gamma}_i}{\partial \sigma}(\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}. The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.

@@

\todo[inline]{Scalable diagonal dominance}

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

\begin{definition}\label{def:SDD}
	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^h |a_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
\end{definition}

The set of scalable diagonally dominant matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $SDD_h$. Let
		\begin{equation}\label{eq:}
			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in SDD_h\}
		\end{equation}
be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$. If the MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rl}
SDSOS_l:=\underset{}{\min} & t \\
\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}

As shown in \cite{AhmadiHall2016} if there exists a solution to \eqref{eq:DSOS} with $l=0$, then

\begin{algorithm}
        \caption{Some alg}
        \begin{algorithmic}[1]	
            \REQUIRE $U_0=I$
            \STATE d = a + b + c
            \STATE d = d/2
            \STATE d = d/3
            \RETURN d
        \end{algorithmic}
    \end{algorithm}

>>>>

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $c:[0,1]\to\mathbb{R}^n$ connecting $x_0=c(0)$ to $x_1=c(1)$. The \emph{length} and \emph{energy} of $c$ are, respectively, defined by the values
\begin{align*}
	\ell(\gamma)=&\ \int_0^1\left|c_s(s)\right|_{c(s)}\,ds\\
	e(\gamma)=&\ \int_0^1V\left(c(s),c_s(s)\right)\,ds\;,
\end{align*}
where the notation $c_s$ stands for the derivative $\tfrac{\partial c}{\partial s}$. The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{c\in\Gamma(x_0,x_1)}\ell(c)\;.
\end{equation}

@@

Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them. This implies that the solution $k^\ast$ to the integral equation
\begin{equation}\label{eq:contracting feedback law}
	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the energy of any curve $c:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		e(c)=\int_0^1\sum_{i=1}^N V_i\left(c_i(s_i),\frac{\partial c_i}{\partial s_i}(s_i)\right)\,ds\;.
	\end{equation}

	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$. Consequently,
	\begin{equation*}
		\gamma_i=\arg\inf e(c_i)\Leftrightarrow\gamma=\arg\inf\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{equation*}
	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.

	From Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
	\begin{align*}
		\gamma_i=\arg\inf_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
	\end{align*}
	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.

@@

	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

@@

	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} which can be employed to design a distributed controller for system~\eqref{eq:general system}.

Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}. The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.

@@

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the search for the matrix $F$ is restricted to have some structure on the diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

\begin{definition}\label{def:SDD}
	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
\end{definition}

The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
		\begin{align*}
			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=U^\top DU,\\
			 D\in SDD_h\}
		\end{align*}
be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$.

Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be cast into the following programming
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rl}
SDSOS_l:=\underset{}{\min} & t^2 \\
\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)
\end{array}
\end{equation}
which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.
